---
title: "User study"
author: "Jeroen O., Niels V.B., Robbe C. & Sebastiano V."
date: "December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(dplyr)
library(ez)
database <- read.csv("database.csv")
#Verwijder de kolom "id".
database$id = NULL

themeData <- database[database$theme == 1, ]
noThemeData <- database[database$theme == 0, ]

nbUsers <- length(unique(database$user))
themeNbUsers <- length(unique(themeData$user))
noThemeNbUsers <- length(unique(noThemeData$user))

usersFinishedLevel9 <- length(unique(database[database$won == 1 & database$level == 9,]$user))

controlThemegroupByUser <- themeData %>% 
                             group_by(user)
themeGroupByUserMinTimestamp <- themeData %>% 
                             group_by(user) %>% 
                             slice(which.min(timeStamp))
themegroupByUser <- themeData %>% 
                             group_by(user)


noThemeGroupByUserMinTimestamp <- noThemeData %>% 
                             group_by(user) %>% 
                             slice(which.min(timeStamp))
themeNotLevel1LoggedFirst <- themeGroupByUserMinTimestamp[themeGroupByUserMinTimestamp$level != 1, ]
noThemeNotLevel1LoggedFirst <- noThemeGroupByUserMinTimestamp[noThemeGroupByUserMinTimestamp$level != 1, ]

userTimestamps <- subset(database, select = c(user, timeStamp))

days <- format(as.Date(userTimestamps$timeStamp,format="%Y-%m-%d"), "%Y-%m-%d")

controlUserDaysTimestamps <- cbind(userTimestamps, days)

userDays <- unique(subset(controlUserDaysTimestamps, select = c(user, days)))

nbUsersPerDay <- data.frame(table(userDays$days))

groupByUserMinTimestamp <- database %>% 
                             group_by(user) %>% 
                             slice(which.min(timeStamp))

model <- ezANOVA(data = groupByUserMinTimestamp, dv = .(startTime), wid = .(user), within = .(theme), detailed = TRUE)
print(model)

newDays <- format(as.Date(groupByUserMinTimestamp$timeStamp,format="%Y-%m-%d"), "%Y-%m-%d")

controlNewUserDaysTimestamps <- cbind(groupByUserMinTimestamp, day = format(as.Date(groupByUserMinTimestamp$timeStamp,format="%Y-%m-%d"), "%Y-%m-%d"))

newUserDays <- unique(subset(controlNewUserDaysTimestamps, select = c(user, day)))

nbNewUsersPerDay <- data.frame(table(newUserDays$day))


Losses <- database[database$won == 0, ]
Wins <- database[database$won == 1, ]
LossesLevel2 <- Losses[Losses$level == 2, ]
WinsLevel2 <- Wins[Wins$level == 2, ]

#de hoeveelheid keren dat je gemiddeld verloor voor je level 2 won
FirstWinLevel2 <- aggregate(timeStamp ~ user, WinsLevel2, function(x) min( as.POSIXct(x)))
joinWinAndLossTableLevel2 <- LossesLevel2 %>% inner_join(FirstWinLevel2, by='user')
LossesBeforefirstWinLevel2 <- filter(joinWinAndLossTableLevel2,as.POSIXct(timeStamp.x) < as.POSIXct(timeStamp.y))
nbLossesBeforefirstWinLevel2 <- count(LossesBeforefirstWinLevel2, user)
meanLevel2<- summarise(nbLossesBeforefirstWinLevel2,n = mean(n))

#de hoeveelheid keren dat je gemiddeld verloor voor je level 3 won
LossesLevel3 <- Losses[Losses$level == 3, ]
WinsLevel3 <- Wins[Wins$level == 3, ]
FirstWinLevel3 <- aggregate(timeStamp ~ user, WinsLevel3, function(x) min( as.POSIXct(x)))
joinWinAndLossTableLevel3 <- LossesLevel3 %>% inner_join(FirstWinLevel3, by='user')
LossesBeforefirstWinLevel3 <- filter(joinWinAndLossTableLevel3,as.POSIXct(timeStamp.x) < as.POSIXct(timeStamp.y))
nbLossesBeforefirstWinLevel3 <- count(LossesBeforefirstWinLevel3, user)
meanLevel3<- summarise(nbLossesBeforefirstWinLevel3,n = mean(n))


#win/loss ratio
Level3 <- database[database$level == 3, ]
FirstTryLevel3 <- aggregate(timeStamp ~ user, Level3, function(x) min( as.POSIXct(x)))
FirstTryLevel3Complete <- FirstTryLevel3 %>% inner_join(Level3, by='user')
FirstTryLevel3Correct <- filter(FirstTryLevel3Complete, as.POSIXct(timeStamp.x) == as.POSIXct(timeStamp.y))
Level3FirstLoss <- FirstTryLevel3Correct[FirstTryLevel3Correct$won == 0, ]
Level3FirstWin <- FirstTryLevel3Correct[FirstTryLevel3Correct$won == 1, ]


nbOfFirstTryLevel3Loss <- length(unique(Level3FirstLoss$user))

nbOfFirstTryLevel3Win <- length(unique(Level3FirstWin$user))

```
Nb Of Users: `r nbUsers`

Nb Of Theme Users: `r themeNbUsers`

Nb Of No Theme Users: `r noThemeNbUsers`

Nb Of Switched Users haha: `r themeNbUsers + noThemeNbUsers - nbUsers`

Switched Users: `r unique(themeData$user[themeData$user %in% noThemeData$user])`
```{r}

```

Nb of users lvl 1 not first logged: `r nrow(themeNotLevel1LoggedFirst)`

Users lvl 1 not first logged: `r themeNotLevel1LoggedFirst$user`

Nb of users lvl 1 not first logged: `r nrow(noThemeNotLevel1LoggedFirst)`

Users lvl 1 not first logged: `r noThemeNotLevel1LoggedFirst$user`

Nb Of Entries: `r nrow(database)`

Nb Of Theme Entries: `r nrow(themeData)`

Nb Of No Theme Entries: `r nrow(noThemeData)`

average loss before each Win in level 2: `r meanLevel2$n[[1]]`

average loss before each Win in level 3: `r meanLevel3$n[[1]]`

average first Try win/loss ratio in level 3: `r nbOfFirstTryLevel3Win/nbOfFirstTryLevel3Loss`

Nb of users that finished the game: `r usersFinishedLevel9`
