---
title: "User study"
author: "Jeroen O., Niels V.B., Robbe C. & Sebastiano V."
date: "December 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(dplyr)
database <- read.csv("database.csv")
#Verwijder de kolom "id".
database$id = NULL

themeData <- database[database$theme == 1, ]
noThemeData <- database[database$theme == 0, ]
nbUsers <- length(unique(database$user))
themeNbUsers <- length(unique(themeData$user))
noThemeNbUsers <- length(unique(noThemeData$user))
themeGroupByUserMinTimestamp <- themeData %>% 
                             group_by(user) %>% 
                             slice(which.min(timeStamp))

Wins <- database[database$won == 1]
Losses <- database[database$won == 0]
themegroupByUser <- themeData %>% 
                             group_by(user)

```
Nb Of Users: `r nbUsers`

Nb Of Theme Users: `r themeNbUsers`

Nb Of No Theme Users: `r noThemeNbUsers`

Nb Of Switched Users haha: `r themeNbUsers + noThemeNbUsers - nbUsers`

Switched Users: `r unique(themeData$user[themeData$user %in% noThemeData$user])`

Users lvl 1 not first logged: 

Nb Of Entries: `r nrow(database)`

Nb Of Theme Entries: `r nrow(themeData)`

Nb Of No Theme Entries: `r nrow(noThemeData)`

Win-loss ratio: `r nrow(Wins)/nrow(nbLosses)` 
